---
title: "data_reporting_2_master"
author: "Eric Harkleroad, Natalie Drum, Pierce Panagakos, Jack Rasiel"
date: "4/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load in the required packages to clean the data

```{r}
library(tidyverse)
library(vembedr)
library(janitor)
library(dplyr)
library(tidycensus)
library(censusxy)
library(lubridate)
library(sf)


census_api_key("549950d36c22ff16455fe196bbbd01d63cfbe6cf")

```
####--- West Virginia ---####

# Read in the raw WV data

```{r}
new_retailer_data <- read.csv("./data/wv/new_retailer_list.csv") %>%
  clean_names()
  #mutate(id = as.character(i_id))


retailer_sales_data <- read.csv("./data/wv/retailer_sales_data.csv") %>%
  mutate_all(funs(ifelse(is.na(.), 0, .))) %>%
  clean_names() %>%
  rename(id = retailer_id) %>%
  mutate(week_ending = as_date (week_ending, format = "%m/%d/%y")) %>%
  mutate(year_name = year(week_ending)) %>%
  mutate(year_name = as.character(year_name)) %>%
  select(-week_ending) %>%
  mutate(id = as.character(id)) %>%
  select(-lotto_america, -all_star_bonus, -just_the_jackpot, -mega_million, -mega_plier) %>%
  #mutate(lotto_america = as.numeric(lotto_america), mega_million = as.numeric(mega_million), mega_plier = as.numeric(mega_plier)) %>%
  mutate(across(where(is.numeric), ~replace_na(.x))) %>%
  select(id, year_name, everything()) %>%
  mutate(all_games_total = instant + daily_3 + daily_4 + cash_25 + hot_lotto + sizzler + powerball + powerplay) %>%
  select(id, year_name, all_games_total) %>%
  group_by(id, year_name) %>%
  summarise(all_games_total = sum(all_games_total)) %>%
  mutate(avg_per_week = all_games_total/52)
  ####




```

# Check for missing data in CSVs given by the agency

```{r}

# inner join of retailer ids to find locations

joined_ids <- retailer_sales_data %>%
  inner_join(new_retailer_data)


```




####---Connecticut Part 1---####

## Loading in raw CT data for 2016 & 2017
```{r}

#Read in raw data

ct_2016_retailer<-read_csv("./data/ct/ct_2016_retailer.csv")%>%
  mutate(store_id=as.character(store_id))

ct_2017_retailer<-read_csv("./data/ct/ct_2017_retailer.csv")%>%
  mutate(store_id=as.character(store_id))


ct_2016<-read_csv("data/ct/ct_2016_sales.csv")%>%
 
  row_to_names(row_number=1)%>%
  mutate(sales_date=as_date(sales_date,format="%m/%d/%y"))%>%
  mutate(year=year(sales_date))%>%
  mutate(across(play3_sales:keno_sales,~as.numeric(.x)))%>%
  group_by(store_id,year)%>%
  summarise(across(play3_sales:keno_sales,~sum(.x)))%>%
  left_join(ct_2016_retailer)%>%
  mutate(store_zipcode=str_pad(store_zipcode,5,side="left",pad="0"))%>%
  

ct_2017<-read_csv("data/ct/ct_2017_sales.csv")%>%
  
  row_to_names(row_number=1)%>%
  mutate(sales_date=as_date(sales_date,format="%m/%d/%y"))%>%
  mutate(year=year(sales_date))%>%
  mutate(across(play3_sales:keno_sales,~as.numeric(.x)))%>%
  group_by(store_id,year)%>%
  summarise(across(play3_sales:keno_sales,~sum(.x)))%>%
  left_join(ct_2017_retailer)%>%
  mutate(store_zipcode=str_pad(store_zipcode,5,side="left",pad="0"))%>%
 

ct_sales<-ct_2016%>%
  bind_rows(ct_2017)


  ###This Mutate is not working
mutate(all_games_total=play3_sales+play4_sales+lotto_sales+cash5_sales+powerball_sales+midday3_sales+midday4sales+lucky_sales+instant_sales+mega_sales+superdraw_sales+fivecc_sales+llinksd_sales+llinksn_sales+keno_sales)%>%
  group_by(id, year_name)%>%
  summarise(all_games_total=sum(all_games_total))%>%

mutate(average_sales_per_week=all_games_total/52)


```

```{r}
CTLottery_Sales_Calendar_2018_ALL_Retailers<-read_csv("./data/ct/CTLottery_Sales_Calendar_2018_ALL_Retailers.csv")
row_to_names(row_number=1)%>%
  mutate(sales_date=as_date(sales_date,format="%m/%d/%Y"))%>%
  mutate(year=year(sales_date))%>%
  mutate(across(play3_sales:keno_sales,~as.numeric(.x)))%>%
  group_by(store_id,year)%>%
  summarise(across(play3_sales:keno_sales,~sum(.x)))%>%
  left_join (CTLottery_Retailer_List_Calendar_2018)
```



```{r}
CTLottery_Sales_Calendar_2019_ALL_Retailers_1_<-read_csv("./data/ct/CTLottery_Sales_Calendar_2019_ALL_Retailers.csv")
row_to_names(row_number=1)%>%
  mutate(sales_date=as_date(sales_date,format="%m/%d/%Y"))%>%
  mutate(year=year(sales_date))%>%
  mutate(across(play3_sales:keno_sales,~as.numeric(.x)))%>%
  group_by(store_id,year)%>%
  summarise(across(play3_sales:keno_sales,~sum(.x)))%>%
  left_join (CTLottery_Retailer_List_Calendar_2019)
```
```{r}

```

```{r}
CTLottery_Sales_Calendar_2020_ALL_Retailers<-read_csv("./data/ct/CTLottery_Sales_Calendar_2020_ALL_Retailers.csv")
row_to_names(row_number=1)%>%
  mutate(sales_date=as_date(sales_date,format="%m/%d/%Y"))%>%
  mutate(year=year(sales_date))%>%
  mutate(across(play3_sales:keno_sales,~as.numeric(.x)))%>%
  group_by(store_id,year)%>%
  summarise(across(play3_sales:keno_sales,~sum(.x)))%>%
  left_join (CTLottery_Retailer_List_Calendar_2020)
```


## Get data for median household income for each county in Connecticut in 2016.

```{r}
ct_county_median_household_income <- get_acs(geography = "county", state="CT",
              variables="B19013_001", year=2016, geometry = FALSE )

ct_county_median_household_income

```

## Get data for median household income for each county in Connecticut in 2017.
```{r}
ct_county_median_household_income <- get_acs(geography = "county", state="CT",
              variables="B19013_001", year=2017, geometry = FALSE )

ct_county_median_household_income

```


####---Illinois---####
## Loading in raw data
```{r}
illinois_sales_data <- read_csv('./data/il/illinois_sales_data.csv')

# NOTE:  the data does not appear to need any cleaning!  See scripts/illinois_data.py

# Cast cols to appropriate types:
illinois_sales_data <- illinois_sales_data %>%
  mutate(
    instant_sales = as.numeric(gsub('\\$|,', '',instant_sales)),
    pick_3_sales = as.numeric(gsub('\\$|,', '',pick_3_sales)),
    pick_4_sales = as.numeric(gsub('\\$|,', '',pick_4_sales)),
    LDL_sales = as.numeric(gsub('\\$|,', '',LDL_sales)),
    lotto_sales = as.numeric(gsub('\\$|,', '',lotto_sales)),
    MM_sales = as.numeric(gsub('\\$|,', '',MM_sales)),
    PB_sales = as.numeric(gsub('\\$|,', '',PB_sales)))
```

## Get data for median household income for each county in Illinois in 2016.

```{r}
il_county_median_household_income <- get_acs(geography = "county", state="IL",
              variables="B19013_001", year=2016, geometry = FALSE )

il_county_median_household_income

```


####---Loading Census Data---####

```{r}
acs_variables <- load_variables(2016, "acs5")

## Get list of states (Exclude non-states, except DC)
states <- fips_codes %>%
  select(state) %>%
  distinct() %>%
  head(51) %>%
  as_vector()

# Get ZCTA data for all states   
zcta_stats <- get_acs(geography = "zcta", variables = c( "B01001_001","B02001_002","B02001_003","B02001_004","B03001_003","B06012_002","B19013_001"), year = 2018) %>%
  select(GEOID, variable, estimate) %>%
  pivot_wider(names_from=variable, values_from=estimate) %>%
  rename(
    total_pop = B01001_001,
    white_pop = B02001_002,
    black_pop = B02001_003,
    native_pop = B02001_004,
    hispanic_pop = B03001_003,
    poverty_pop = B06012_002,
    median_income = B19013_001
  ) %>%
  mutate(pct_white = round(white_pop/total_pop,2)*100,
         pct_nonwhite = 100-round(white_pop/total_pop,2)*100,
         pct_black = round(black_pop/total_pop,2)*100,
         pct_native = round(native_pop/total_pop,2)*100,
         pct_hispanic = round(hispanic_pop/total_pop,2)*100,
         pct_poverty = round(poverty_pop/total_pop,2)*100
         ) %>%
  clean_names() %>%
  mutate(fips_code_state = str_sub(geoid,start=1L,end=2L),
         geoid=str_sub(geoid, start=3L,end=7L)) %>%
  select(fips_code_state,geoid,-ends_with("pop"), starts_with("pct"),median_income)

# Get census tract data for all states
census_tract_stats <- get_acs(geography = "tract", variables = c( "B01001_001","B02001_002","B02001_003","B02001_004","B03001_003","B06012_002","B19013_001"), state=states,year = 2017) %>%
  select(GEOID, variable, estimate) %>%
  pivot_wider(names_from=variable, values_from=estimate) %>%
  rename(
    total_pop = B01001_001,
    white_pop = B02001_002,
    black_pop = B02001_003,
    native_pop = B02001_004,
    hispanic_pop = B03001_003,
    poverty_pop = B06012_002,
    median_income = B19013_001
  ) %>%
  mutate(pct_white = round(white_pop/total_pop,2)*100,
         pct_nonwhite = 100-round(white_pop/total_pop,2)*100,
         pct_black = round(black_pop/total_pop,2)*100,
         pct_native = round(native_pop/total_pop,2)*100,
         pct_hispanic = round(hispanic_pop/total_pop,2)*100,
         pct_poverty = round(poverty_pop/total_pop,2)*100
         ) %>%
  clean_names() %>%
  select(geoid,-ends_with("pop"), starts_with("pct"),median_income)
```

####################################
########### QUESTION 1 #############
####################################

#```{r}
##  DO_QUESTION_1: generate the sales-vs-income and sales-vs-race plots for a given state.
##
## PARAMETERS:
##     fips_code:  int - the fips_code for this state
##     data:       The lottery salees dataframe for the state.  
##                 Each row must be a unique establishment/retailer.
##                 (i.e., if your data has one row per week/year for retailers,
##                   aggregate all of those rows into a single row for that retailer!)
##                 MUST HAVE these columns (rename to match these names exactly):
##                !!!!   estab_name, estab_zip, avg_sales_per_week  !!!!
##                   (can have other columns, but these are the ones the function uses)
##
## RETURNS:
##   plots:    a list with the two plots.  You can access them like this:
##               by_income = plots$by_income
##               by_race = plots$by_race
#do_question_1 <- function(fips_code, data) {
#  # 1- get geocodes for each establishment.  Get zip code / tract for each geocode.
#        # in: fips_code, data
#        # out: data, with new column "zip"
#
#  ############
#  # 2- group establishments by zip code/ tract.
#        # out:  estabs_by_zip: "data" but grouped by zip.
# estabs_by_zip <- data %>% # your code here!
#
#  ############
#  # 3- for each zip code group: sum sales data across establishments in that group.
#
#  # Result: total_sales_per_zip, a table where each row is a zip code, with its aggregate sales data.
#  total_sales_per_zip <- estabs_by_zip %>%
#
#  ############
#  # 4- divide weekly_sales by population of that zip code
#
#  # Result:  total_sales_per_zip with new column "weekly_sales_per_capita"
#  total_sales_per_zip <- total_sales_per_zip %>%
#
#  ############
#  # 5- get demographic data: racial and income
#  #         - (TODO - how define "non-white areas")
#  #         - (TODO - how define "low income areas")
#  # Result:  total_sales_per_zip with new columns for income and race demographics
#  total_sales_per_zip <- total_sales_per_zip %>%
#
#  ############
#  # 6- plot!
#  #        - scatterplot:  % non-white vs lottery sales
#  #        - scatterplot:  income vs lottery sales
#  # Result:  plots of the data from total_sales_per_zip.
#  #          Most obvious choice would be a simple scatterplot, but, of course,
#  #           you can do what you like!
#  total_sales_per_zip <- total_sales_per_zip %>%
#  plot_by_income <- # the plot
#  plot_by_race<- # the plot
#
#  # The return values:
#  plots <- list("by_income" = plot_by_income, "by_race" = plot_by_race)
#}
#```

```{r}
# WV Census

## Get list of states (Exclude non-states, except DC)
states <- fips_codes %>%
  select(state) %>%
  distinct() %>%
  head(51) %>%
  as_vector()

# Get ZCTA data for all states   
zcta_stats <- get_acs(geography = "zcta", variables = c( "B01001_001","B02001_002","B02001_003","B02001_004","B03001_003","B06012_002","B19013_001"), year = 2018) %>%
  select(GEOID, variable, estimate) %>%
  pivot_wider(names_from=variable, values_from=estimate) %>%
  rename(
    total_pop = B01001_001,
    white_pop = B02001_002,
    black_pop = B02001_003,
    native_pop = B02001_004,
    hispanic_pop = B03001_003,
    poverty_pop = B06012_002,
    median_income = B19013_001
  ) %>%
  mutate(pct_white = round(white_pop/total_pop,2)*100,
         pct_nonwhite = 100-round(white_pop/total_pop,2)*100,
         pct_black = round(black_pop/total_pop,2)*100,
         pct_native = round(native_pop/total_pop,2)*100,
         pct_hispanic = round(hispanic_pop/total_pop,2)*100,
         pct_poverty = round(poverty_pop/total_pop,2)*100
         ) %>%
  clean_names() %>%
  mutate(fips_code_state = str_sub(geoid,start=1L,end=2L),
         geoid=str_sub(geoid, start=3L,end=7L)) %>%
  select(fips_code_state,geoid, total_pop, starts_with("pct"),median_income)

wv_census <- zcta_stats %>%
  filter(fips_code_state == 54) %>%
  rename(l_zip = geoid) %>%
  mutate(l_zip = as.numeric(l_zip))


#lets join

wv_census_joined <- joined_ids %>%
  group_by(id, l_zip) %>%
  summarise(all_games_total = sum(all_games_total)) %>%
  inner_join(wv_census) %>%
  ungroup() %>%
  select(id, all_games_total, l_zip, pct_white, pct_poverty, median_income, total_pop) %>%
  mutate(income_bucket = ntile(median_income, 5),
         white_bucket = ntile(pct_white, 5),
         poverty_bucket = ntile(pct_poverty, 5),
         pop_bucket = ntile(total_pop, 5))



wv_income_bucket <- wv_census_joined %>%
  group_by(income_bucket) %>%
  summarise(mean_sales = mean(all_games_total),
            max_income = max(median_income),
            )

wv_white_bucket <- wv_census_joined %>%
  group_by(white_bucket) %>%
  summarise(mean_sales = mean(all_games_total),
            max_white = max(pct_white),
            )


wv_poverty_bucket <- wv_census_joined %>%
  group_by(poverty_bucket) %>%
  summarise(mean_sales = mean(all_games_total),
            max_poverty = max(pct_poverty),
            )

wv_pop_bucket <- wv_census_joined %>%
  group_by(pop_bucket) %>%
  summarise(mean_sales = mean(all_games_total),
            max_pop = max(total_pop),
            )


# Answer: In looking at the data both overall and standardizing for population, I do not see a correlation between lottery sales and race, poverty or median income.
# (Jack's note) WV is an unusual case because it is so racially homogeneous:  ~93 pct non-hispanic white.  So there's probably not much reason to do marketing targeted on race.  Also, many of those white people are poor -- so the correlation between race and income correlation is probably weaker than in more diverse states. 
```


##############################################


```{r}

#  DO_QUESTION_1: generate the sales-vs-income and sales-vs-race plots for a given state.
#
# PARAMETERS:
#     fips_code:  int - the fips_code for this state
#     data:       The lottery salees dataframe for the state.  
#                 Each row must be a unique establishment/retailer.
#                 (i.e., if your data has one row per week/year for retailers,
#                   aggregate all of those rows into a single row for that retailer!)
#                 MUST HAVE these columns (rename to match these names exactly):
#                !!!!   estab_name, estab_zip, avg_sales_per_week  !!!!
#                   (can have other columns, but these are the ones the function uses)
#
# RETURNS:
#   plots:    a list with the two plots.  You can access them like this:
#               by_income = plots$by_income
#               by_race = plots$by_race
do_question_1 <- function(fips_code, data) {
census <- zcta_stats %>%
  filter(fips_code_state == fips_code) %>%
  rename(l_zip = geoid) %>%
  mutate(l_zip = as.numeric(l_zip))


#lets join

census_joined <- joined_ids %>%
  group_by(id, l_zip) %>%
  summarise(avg_sales_per_week = sum(avg_sales_per_week)) %>%
  inner_join(census) %>%
  ungroup() %>%
  select(id, avg_sales_per_week, l_zip, pct_white, pct_poverty, median_income, total_pop) %>%
  mutate(income_bucket = ntile(median_income, 5),
         white_bucket = ntile(pct_white, 5),
         poverty_bucket = ntile(pct_poverty, 5),
         pop_bucket = ntile(total_pop, 5))



income_bucket <- census_joined %>%
  group_by(income_bucket) %>%
  summarise(mean_sales = mean(avg_sales_per_week),
            max_income = max(median_income),
            )

white_bucket <- census_joined %>%
  group_by(white_bucket) %>%
  summarise(mean_sales = mean(avg_sales_per_week),
            max_white = max(pct_white),
            )


poverty_bucket <- census_joined %>%
  group_by(poverty_bucket) %>%
  summarise(mean_sales = mean(avg_sales_per_week),
            max_poverty = max(pct_poverty),
            )

pop_bucket <- census_joined %>%
  group_by(pop_bucket) %>%
  summarise(mean_sales = mean(avg_sales_per_week),
            max_pop = max(total_pop),
            )

  buckets <- list("income" = income_bucket, "white" = white_bucket,"poverty" = poverty_bucket, "population" = pop_bucket)
}
```

#### ILLINOIS ####
# Question 1: Are lottery ticket sales (overall or population adjusted) higher at retailers located in low-income or non-white areas?

```{r}
# Format data for the function:
# REMEMBER, the function expects these columns: estab_name, estab_zip, avg_sales_per_week
# Rename cols to match expectations:  
illinois_sales_data <- illinois_sales_data %>%
  mutate(estab_name = retailer_name, estab_zip = retailer_address_zip_code)

# Compute sales per week
illinois_sales_data_agg <- illinois_sales_data %>% group_by(retailer_id) %>%
  summarise(total_sales = sum(instant_sales, pick_3_sales , pick_4_sales ,
                        LDL_sales, lotto_sales, MM_sales, PB_sales),
            num_years_present_in_data = n() ) %>%
  mutate(avg_sales_per_week = total_sales / (52 * num_years_present_in_data))

# Now, generate the plots via the function call!
buckets <- do_question_1(17, illinois_sales_data_agg) # IL's FIPS code is 17
# Access the different summary stats like so:
glimps(buckets$income)
## show the plots:
#plots$by_income
#plots$by_race
```

#### WEST VIRGINIA ####
# Question 1: Are lottery ticket sales (overall or population adjusted) higher at retailers located in low-income or non-white areas?

```{r}
#wv_zcta_stats <- zcta_stats %>%
#  # Select only WV Zcta data
#  filter(fips_code_state == "54")
#
#joined_wv_data <- wv_zcta_stats %>%
#  inner_join(wv_zcta_stats, retailer_sales_data, by = "geoid")
```

#### Connecticut ####
# Question 1: Are lottery ticket sales (overall or population adjusted) higher at retailers located in low-income or non-white areas?

```{r}
# CT Census
## Get list of states (Exclude non-states, except DC)
states <- fips_codes %>%
  select(state) %>%
  distinct() %>%
  head(51) %>%
  as_vector()
# Get ZCTA data for all states   
zcta_stats <- get_acs(geography = "zcta", variables = c( "B01001_001","B02001_002","B02001_003","B02001_004","B03001_003","B06012_002","B19013_001"), year = 2018) %>%
  select(GEOID, variable, estimate) %>%
  pivot_wider(names_from=variable, values_from=estimate) %>%
  rename(
    total_pop = B01001_001,
    white_pop = B02001_002,
    black_pop = B02001_003,
    native_pop = B02001_004,
    hispanic_pop = B03001_003,
    poverty_pop = B06012_002,
    median_income = B19013_001
  ) %>%
  mutate(pct_white = round(white_pop/total_pop,2)*100,
         pct_nonwhite = 100-round(white_pop/total_pop,2)*100,
         pct_black = round(black_pop/total_pop,2)*100,
         pct_native = round(native_pop/total_pop,2)*100,
         pct_hispanic = round(hispanic_pop/total_pop,2)*100,
         pct_poverty = round(poverty_pop/total_pop,2)*100
         ) %>%
  clean_names() %>%
  
mutate(fips_code_state = str_sub(geoid,start=1L,end=2L),geoid=str_sub(geoid, start=3L,end=7L)) %>%
  select(fips_code_state,geoid, total_pop, starts_with("pct"),median_income)

  
ct_census <- zcta_stats %>%
  filter(fips_code_state == 09) %>%
  rename(l_zip = geoid) %>%
  mutate(l_zip = as.numeric(l_zip))




#lets join

ct_census_joined <- joined_ids %>%
  group_by(id,year_name) %>%
  summarise(all_games_total = sum(all_games_total)) %>%
  inner_join(ct_census) %>%
  ungroup() %>%
  select(id, all_games_total, pct_white, pct_poverty, median_income, total_pop)%>%
  mutate(income_bucket = ntile(median_income, 5),
         white_bucket = ntile(pct_white, 5),
         poverty_bucket = ntile(pct_poverty, 5),
         pop_bucket = ntile(total_pop, 5))
ct_income_bucket <- ct_census_joined %>%
  group_by(income_bucket) %>%
  summarise(mean_sales = mean(all_games_total),
            max_income = max(median_income),
            )
ct_white_bucket <- ct_census_joined %>%
  group_by(white_bucket) %>%
  summarise(mean_sales = mean(all_games_total),
            max_white = max(pct_white),
            )
ct_poverty_bucket <- ct_census_joined %>%
  group_by(poverty_bucket) %>%
  summarise(mean_sales = mean(all_games_total),
            max_poverty = max(pct_poverty),
            )
ct_pop_bucket <- ct_census_joined %>%
  group_by(pop_bucket) %>%
  summarise(mean_sales = mean(all_games_total),
            max_pop = max(total_pop),
            )
```

#### ILLINOIS ####
# Question 1: Are lottery ticket sales (overall or population adjusted) higher at retailers located in low-income or non-white areas?

```{r}
# Format data for the function:
# REMEMBER, the function expects these columns: estab_name, estab_zip, avg_sales_per_week
# Rename cols to match expectations:  
illinois_sales_data <- illinois_sales_data %>%
  mutate(estab_name = retailer_name, estab_zip = retailer_address_zip_code)

# Compute sales per week
illinois_sales_data_agg <- illinois_sales_data %>% group_by(retailer_id) %>%
  summarise(total_sales = sum(instant_sales, pick_3_sales , pick_4_sales ,
                        LDL_sales, lotto_sales, MM_sales, PB_sales),
            num_years_present_in_data = n() ) %>%
  mutate(avg_sales_per_week = total_sales / (52 * num_years_present_in_data))

# Now, generate the plots via the function call!
buckets <- do_question_1(17, illinois_sales_data_agg) # IL's FIPS code is 17
# Access the different summary stats like so:
glimpse(buckets$income)
## show the plots:
#plots$by_income
#plots$by_race
```
```

####################################
########### QUESTION 3 #############
####################################


# Jack's brief brainstorm:
#  - how does proportion non-white, or income skew, change over time?
#  - how did the pandemic change lottery-buying habits?  Did the changes effect different groups differently
#      (e.g., did lower income people buy fewer lottery tickets, because their wallets were harder hit 
#      by pandemic-related job loss?)
#  - data limitations:
#    - WV: weekly sales, 2014-07 thru 2020-06
#    - CT: 
#    - IL: *yearly* sales, for 2016 thru 2020
  
#### ILLINOIS ####
# Question 3: Have any of the sales trends we've identified changed over the last few years, especially when comparing trends before and during the pandemic?

```{r}
```

#### WEST VIRGINIA ####
# Question 3: Have any of the sales trends we've identified changed over the last few years, especially when comparing trends before and during the pandemic?

```{r}
```

#### CONNECTICUT ####
# Question 3: Have any of the sales trends we've identified changed over the last few years, especially when comparing trends before and during the pandemic?

```{r}
```
