---
title: "working_ct_data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
# Tidyverse
library(tidyverse)

# Load Tidycensus after installing if necessary
#install.packages(tidycensus)
library(tidycensus)

# Load censusxy for geocoding
# 
library(censusxy)

library(sf)
library(lubridate)


library(janitor)

# Store census API key
# Use mine for now, in the future use yours
census_api_key("549950d36c22ff16455fe196bbbd01d63cfbe6cf")

```


## Loading in raw data 
```{r}

#Read in raw data 

ct_2016_retailer<-read_csv("data_ct/ct_2016_retailer.csv")%>%
  mutate(store_id=as.character(store_id))

ct_2017_retailer<-read_csv("data_ct/ct_2017_retailer.csv")%>%
  mutate(store_id=as.character(store_id))



ct_2016<-read_csv("data_ct/ct_2016_sales.csv")%>%
 
  row_to_names(row_number=1)%>%
  mutate(sales_date=as_date(sales_date,format="%m/%d/%y"))%>%
  mutate(year=year(sales_date))%>%
  mutate(across(play3_sales:keno_sales,~as.numeric(.x)))%>%
  group_by(store_id,year)%>%
  summarise(across(play3_sales:keno_sales,~sum(.x)))%>%
  left_join(ct_2016_retailer)%>%
  mutate(store_zipcode=str_pad(store_zipcode,5,side="left",pad="0"))%>%
  #mutate(all_games_total= play3_sales+play4_sales+lotto_sales+cash5_sales+powerball_sales+midday3_sales+middday4sales+lucky_sales+instant_sales+mega_sales+superdraw_sales+fivecc_sales+llinksd_sales+llinksn_sales+keno_sales)
  #mutate(average_sales_per_week=all_games_total/52)
  
  
ct_2017<-read_csv("data_ct/ct_2017_sales.csv")%>%
  row_to_names(row_number=1)%>%
  mutate(sales_date=as_date(sales_date,format="%m/%d/%y"))%>%
  mutate(year=year(sales_date))%>%
  mutate(across(play3_sales:keno_sales,~as.numeric(.x)))%>%
  group_by(store_id,year)%>%
  summarise(across(play3_sales:keno_sales,~sum(.x)))%>%
  left_join(ct_2017_retailer)%>%
 mutate(store_zipcode=str_pad(store_zipcode,5,side="left",pad="0"))
 #check games in 2017 for games
#mutate(all_games_total= play3_sales+play4_sales+lotto_sales+cash5_sales+powerball_sales+midday3_sales+middday4sales+lucky_sales+instant_sales+mega_sales+superdraw_sales+fivecc_sales+llinksd_sales+llinksn_sales+keno_sales)
  #mutate(average_sales_per_week=all_games_total/52)

ct_sales<-ct_2016%>%
  bind_rows(ct_2017)

```

## Get data for median household income for each county in Connecticut in 2016.

```{r}
ct_county_median_household_income <- get_acs(geography = "county", state="CT",
              variables="B19013_001", year=2016, geometry = FALSE )

ct_county_median_household_income

```

## This function pulls all the avaiable variables for 2012 from the acs, with data from the previous 5 years averaged into a single estimate. 

```{r}
acs_variables <- load_variables(2016, "acs5")
```

# Get a data table with demographic information

```{r}
## Get list of states (Exclude non-states, except DC)
states <- fips_codes %>%
  select(state) %>%
  distinct() %>%
  head(51) %>%
  as_vector() 

# Get ZCTA data for all states   
zcta_stats <- get_acs(geography = "zcta", variables = c( "B01001_001","B02001_002","B02001_003","B02001_004","B03001_003","B06012_002","B19013_001"), year = 2016) %>%
  select(GEOID, variable, estimate) %>%
  pivot_wider(names_from=variable, values_from=estimate) %>%
  rename(
    total_pop = B01001_001,
    white_pop = B02001_002,
    black_pop = B02001_003,
    native_pop = B02001_004,
    hispanic_pop = B03001_003,
    poverty_pop = B06012_002,
    median_income = B19013_001
  ) %>%
  mutate(pct_white = round(white_pop/total_pop,2)*100,
         pct_nonwhite = 100-round(white_pop/total_pop,2)*100,
         pct_black = round(black_pop/total_pop,2)*100,
         pct_native = round(native_pop/total_pop,2)*100,
         pct_hispanic = round(hispanic_pop/total_pop,2)*100,
         pct_poverty = round(poverty_pop/total_pop,2)*100
         ) %>%
  clean_names() %>%
  mutate(fips_code_state = str_sub(geoid,start=1L,end=2L),
         geoid=str_sub(geoid, start=3L,end=7L)) %>%
  select(fips_code_state,geoid,-ends_with("pop"), starts_with("pct"),median_income) 

  
# Get census tract data for all states
census_tract_stats <- get_acs(geography = "tract", variables = c( "B01001_001","B02001_002","B02001_003","B02001_004","B03001_003","B06012_002","B19013_001"), state=states,year = 2016) %>%
  select(GEOID, variable, estimate) %>%
  pivot_wider(names_from=variable, values_from=estimate) %>%
  rename(
    total_pop = B01001_001,
    white_pop = B02001_002,
    black_pop = B02001_003,
    native_pop = B02001_004,
    hispanic_pop = B03001_003,
    poverty_pop = B06012_002,
    median_income = B19013_001
  ) %>%
  mutate(pct_white = round(white_pop/total_pop,2)*100,
         pct_nonwhite = 100-round(white_pop/total_pop,2)*100,
         pct_black = round(black_pop/total_pop,2)*100,
         pct_native = round(native_pop/total_pop,2)*100,
         pct_hispanic = round(hispanic_pop/total_pop,2)*100,
         pct_poverty = round(poverty_pop/total_pop,2)*100
         ) %>%
  clean_names() %>%
  select(geoid,-ends_with("pop"), starts_with("pct"),median_income)


```
## Get data for median household income for each county in Connecticut in 2017.
```{r}
ct_county_median_household_income <- get_acs(geography = "county", state="CT",
              variables="B19013_001", year=2017, geometry = FALSE )

ct_county_median_household_income

```

## This function pulls all the avaiable variables for 2012 from the acs, with data from the previous 5 years averaged into a single estimate. 

```{r}
acs_variables <- load_variables(2017, "acs5")
```

# Get a data table with demographic information for 2017

```{r}
## Get list of states (Exclude non-states, except DC)
states <- fips_codes %>%
  select(state) %>%
  distinct() %>%
  head(51) %>%
  as_vector() 

# Get ZCTA data for all states   
zcta_stats <- get_acs(geography = "zcta", variables = c( "B01001_001","B02001_002","B02001_003","B02001_004","B03001_003","B06012_002","B19013_001"), year = 2017) %>%
  select(GEOID, variable, estimate) %>%
  pivot_wider(names_from=variable, values_from=estimate) %>%
  rename(
    total_pop = B01001_001,
    white_pop = B02001_002,
    black_pop = B02001_003,
    native_pop = B02001_004,
    hispanic_pop = B03001_003,
    poverty_pop = B06012_002,
    median_income = B19013_001
  ) %>%
  mutate(pct_white = round(white_pop/total_pop,2)*100,
         pct_nonwhite = 100-round(white_pop/total_pop,2)*100,
         pct_black = round(black_pop/total_pop,2)*100,
         pct_native = round(native_pop/total_pop,2)*100,
         pct_hispanic = round(hispanic_pop/total_pop,2)*100,
         pct_poverty = round(poverty_pop/total_pop,2)*100
         ) %>%
  clean_names() %>%
  mutate(fips_code_state = str_sub(geoid,start=1L,end=2L),
         geoid=str_sub(geoid, start=3L,end=7L)) %>%
  select(fips_code_state,geoid,-ends_with("pop"), starts_with("pct"),median_income) 

  
# Get census tract data for all states
census_tract_stats <- get_acs(geography = "tract", variables = c( "B01001_001","B02001_002","B02001_003","B02001_004","B03001_003","B06012_002","B19013_001"), state=states,year = 2017) %>%
  select(GEOID, variable, estimate) %>%
  pivot_wider(names_from=variable, values_from=estimate) %>%
  rename(
    total_pop = B01001_001,
    white_pop = B02001_002,
    black_pop = B02001_003,
    native_pop = B02001_004,
    hispanic_pop = B03001_003,
    poverty_pop = B06012_002,
    median_income = B19013_001
  ) %>%
  mutate(pct_white = round(white_pop/total_pop,2)*100,
         pct_nonwhite = 100-round(white_pop/total_pop,2)*100,
         pct_black = round(black_pop/total_pop,2)*100,
         pct_native = round(native_pop/total_pop,2)*100,
         pct_hispanic = round(hispanic_pop/total_pop,2)*100,
         pct_poverty = round(poverty_pop/total_pop,2)*100
         ) %>%
  clean_names() %>%
  select(geoid,-ends_with("pop"), starts_with("pct"),median_income)


```
## Question 1

```{r}
# Question 1: Are lottery ticket sales (overall or population adjusted) higher at retailers located in low-income or non-white areas?

ct_zcta_stats <- zcta_stats %>%
  
  filter(fips_code_state == "09")
```

