---
title: "Data Analysis 01 Template"
author: "Student names here"
date: "3/2/2021"
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction 

In this notebook, we are reverse engineering the story, Fewer Inspectors, More Deaths: The Trump Administration Rolls Back Workplace Safety Inspections, from the Center for Public Integrity [FEWER INSPECTORS, MORE DEATHS: THE TRUMP ADMINISTRATION ROLLS BACK WORKPLACE SAFETY INSPECTIONS](https://publicintegrity.org/politics/system-failure/deaths-cutbacks-workplace-safety-inspections-osha/)

## Load libraries

Loading required libraries for this analysis.

```{r echo=FALSE, message=FALSE}

```
```{r}
# If you are on a new machine you haven't used before, you may need to install these packages before loading.  If that's the case, remove the comment # from in front of the next two lines before running the codeblock, to install the packages before loading.
install.packages('tidyverse')
install.packages('vembedr')
# Load the tidyverse, vembedr
library(tidyverse)
library(vembedr)
```
## Load and Cleaning Data

[In this block of text, describe the source of the data, and write a basic data dictionary for data you are working with]

```{r}
# Load required data
# Path to data should be loaded from folder "data" i.e. read_csv("data/name_of_data.csv")

# Clean required data and prepare for analysis if needed. 


```

## Sentences to Engineer
In this notebook, we are reverse engineering five sentences from the story.

### Sentence 1

* **Sentence text**: “Since 2015, police have killed 26 unarmed women, including Taylor. Of those, 14 were White, seven were Black, four were Hispanic and one’s race was unknown. While about twice as many White women were shot and killed as Black women, White women account for five times the Black female population.”

* **Analysis summary**: Since this article was been written, two more unarmed women were shot and killed by police. So, the true count is 28 unarmed women, not 26. The two most recent deaths were Ashi Babbitt on Jan. 6, 2021 and Evatt Hernandez on Dec. 9, 2020. The race count in the above sentence is very close, but yes, since the article was published, it changed. There are still seven Black women and one woman whose race is unknown, but there are now 15 White women and five Hispanic women. The disparity they point out in the original sentence is still true given the disproportionate population difference between White women and Black women.

```{r}
# Put code to reverse engineer sentence here


# Creates a new dataframe where it filters only for WOMEN who are UNARMED. Arranges them by most recent date of death.
unarmed_women_by_race <- fatal_police_shootings %>%
  filter(gender == "F" & armed == "unarmed") %>%
  arrange(desc(date))

# Creates new dataframe pulling from the dataframe made above. Uses count() function to get a count of how many of each race have died. sort = TRUE displays this count from largest to smallest

counts_of_race <- unarmed_women_by_race %>%
  group_by(race) %>%
  count() %>%
  arrange(desc(n))
  #count(race, race, wt = NULL, sort = TRUE, name = NULL)
  


# Display results of code below this codeblock
unarmed_women_by_race

counts_of_race

# Display results of code below this codeblock

```


### Sentence 2

* **Sentence text**: “Since 2015, Black women have accounted for less than 1 percent of the overall fatal shootings in cases where race was known. But within this small subset, Black women, who are 13 percent of the female population, account for 20 percent of the women shot and killed and 28 percent of the unarmed deaths.”
* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 3

* **Sentence text**: “About 31 percent, or 77, of the 247 women fatally shot by police since 2015 had mental health issues, compared to 22 percent of the 5,362 men killed.”
* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 4

* **Sentence text**: “Since The Washington Post began tracking fatal shootings by police in 2015, officers have fatally shot 247 women out of the more than 5,600 people killed overall.”

* **Analysis summary**: Since the Washington Post began tracking fatal shootings by police in 2015, officers have fatally shot 247 women out of the more than 5,600 people killed overall.

```{r}
# Put code to reverse engineer sentence here:

# Creates a new dataframe where it filters only for WOMEN who are UNARMED. Arranges them by most recent date of death.
unarmed_women_by_race <- fatal_police_shootings %>%
  filter(gender == "F" & armed == "unarmed") %>%
  arrange(desc(date))

# Creates new dataframe pulling from the dataframe made above. Uses count() function to get a count of how many of each race have died. sort = TRUE displays this count from largest to smallest

counts_of_race <- unarmed_women_by_race %>%
  group_by(race) %>%
  count() %>%
  arrange(desc(n))
  #count(race, race, wt = NULL, sort = TRUE, name = NULL)
  


# Display results of code below this codeblock
unarmed_women_by_race

counts_of_race



# Display results of code below this codeblock

```

### Sentence 5

* **Sentence text**: "The starkest difference between men and women is the rate: Women account for about half the population but 4 percent of the killings."

* **Analysis summary**: My findings show that women account for 4.4 percent of killings between male, female and one N/A. My findings are slightly higher than the original question, maybe due to more killings that have happend since this data was published.  There were 5816 men killed, 270 females and 1 N/A. A total of 6,087. Next, divide 270 by 6,087 multiply it by 100 and get 4.44 percent. 


```{r}
# Put code to reverse engineer sentence here

gender_killed <- fatal_police_shootings_data %>%
 group_by(gender) %>%
summarise(amount_killed = n()) %>%
  arrange(desc(amount_killed))

# Display results of code below this codeblock

gender_killed 

```

-30-