---
title: "Data Analysis 01 Template"
author: "Student names here"
date: "3/2/2021"
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction 

In this notebook, we are reverse engineering the story, Fewer Inspectors, More Deaths: The Trump Administration Rolls Back Workplace Safety Inspections, from the Center for Public Integrity [FEWER INSPECTORS, MORE DEATHS: THE TRUMP ADMINISTRATION ROLLS BACK WORKPLACE SAFETY INSPECTIONS](https://publicintegrity.org/politics/system-failure/deaths-cutbacks-workplace-safety-inspections-osha/)

## Load libraries

Loading required libraries for this analysis.

```{r echo=FALSE, message=FALSE}

```
```{r}
# If you are on a new machine you haven't used before, you may need to install these packages before loading.  If that's the case, remove the comment # from in front of the next two lines before running the codeblock, to install the packages before loading.
install.packages('tidyverse')
install.packages('vembedr')
# Load the tidyverse, vembedr
library(tidyverse)
library(vembedr)
```
## Load and Cleaning Data



```{r}
# Load required data
# Path to data should be loaded from folder "data" i.e. read_csv("data/name_of_data.csv")

# Clean required data and prepare for analysis if needed. 


```

## Sentences to Engineer
In this notebook, we are reverse engineering five sentences from the story.

### Sentence 1

* **Sentence text**: “Since 2015, police have killed 26 unarmed women, including Taylor. Of those, 14 were White, seven were Black, four were Hispanic and one’s race was unknown. While about twice as many White women were shot and killed as Black women, White women account for five times the Black female population.”

* **Analysis summary**: Since this article was been written, two more unarmed women were shot and killed by police. So, the true count is 28 unarmed women, not 26. The two most recent deaths were Ashi Babbitt on Jan. 6, 2021 and Evatt Hernandez on Dec. 9, 2020. The race count in the above sentence is very close, but yes, since the article was published, it changed. There are still seven Black women and one woman whose race is unknown, but there are now 15 White women and five Hispanic women. The disparity they point out in the original sentence is still true given the disproportionate population difference between White women and Black women.

```{r}
# Put code to reverse engineer sentence here


# Creates a new dataframe where it filters only for WOMEN who are UNARMED. Arranges them by most recent date of death.
unarmed_women_by_race <- fatal_police_shootings %>%
  filter(gender == "F" & armed == "unarmed") %>%
  arrange(desc(date))

# Creates new dataframe pulling from the dataframe made above. Uses count() function to get a count of how many of each race have died. sort = TRUE displays this count from largest to smallest

counts_of_race <- unarmed_women_by_race %>%
  group_by(race) %>%
  count() %>%
  arrange(desc(n))
  #count(race, race, wt = NULL, sort = TRUE, name = NULL)
  


# Display results of code below this codeblock
unarmed_women_by_race

counts_of_race

# Display results of code below this codeblock

```


### Sentence 2

* **Sentence text**: “Since 2015, Black women have accounted for less than 1 percent of the overall fatal shootings in cases where race was known. But within this small subset, Black women, who are 13 percent of the female population, account for 20 percent of the women shot and killed and 28 percent of the unarmed deaths.”
* **Analysis summary**: I was able to confirm their first finding (Black women account for less than 1% of total fatal shootings) -- they make up 0.8%. Their second finding, that Black women account for 20% of all women fatally shot by police, I was unable to confirm. I got 18%, which is close. I suspect this is because the data has changed since the original article came out. Finally, I was unable to confirm their third finding, that Black women account for 28% of unarmed women deaths. The actual sentence is misleading, since I originally thought they meant 28% of all unarmed deaths regardless of gender. Looking at unarmed Black women to only unarmed women, we see a closer percentage, 25%. I suspect this difference is also because of the change in data since publication.


```{r}
# Put code to reverse engineer sentence here
# Step 1: Get % of Black women compared to all people in the dataset

percent_black_women_killed_to_total <- fatal_police_shootings %>%
  group_by(gender, race) %>%
  count() %>%
  ungroup() %>%
  mutate(total_shootings = sum(n)) %>%
  mutate(percent_of_total_shootings = (n/total_shootings)*100) %>%
  filter(gender == "F" & race == "B")


# Step 2: Get % of Black women compared to all women in the dataset

percent_black_women_killed_to_women <- fatal_police_shootings %>%
  group_by(gender, race) %>%
  count() %>%
  ungroup() %>%
  filter (gender == "F") %>%
  mutate(total_women_killed = sum(n)) %>%
  mutate(percent_of_total_women_killed = (n/total_women_killed)*100) %>%
  filter(gender == "F" & race == "B")

# Step 3: Get % of Black unarmed women compared to all unarmed women in the dataset.

percent_unarmed_black_women_killed_to_unarmed_women <- fatal_police_shootings %>%
  # First, group the data by race, gender and armed variables. Those are all of the variables we're considering for this question.
  group_by(race, gender, armed) %>%
  # Next, generate counts -- the n column -- of each race, gender & armed combo
  count() %>%
  # Now that we have the number of each group combo, we need to get the total of unarmed women, so we'll ungroup and filter for unarmed women.
  ungroup() %>%
  filter(gender == "F" & armed == "unarmed") %>%
  # To get the total, we'll mutate to create a column called "total_unarmed_women_killed" that equals the sum of all of the values in the n column (the counts).
  mutate(total_unarmed_women_killed = sum(n)) %>%
  # We see now that 28 unarmed women have been killed total since 2015. That total is next to every row, so now we just need to calculate the percentage by dividing n with the totals. I'll do this by creating a new column with mutate that represents the percentage.
  mutate(percent_of_total_unarmed_women_killed = (n/total_unarmed_women_killed)*100) %>%
  # Now, we've got the % of each race of unarmed women are compared to the total # of unarmed women. Let's look at just Black women to answer the last question.
  filter(gender == "F" & race == "B")



# Display results of code below this codeblock

# Claim 1: Black women make up 0.80% of all fatal police shootings. The article says this, that they make up less than 1% of the total.
percent_black_women_killed_to_total

# Claim 2: Black women make up 18.15% of women fatally shot by police. The article says they make up 20% of all women fatally shot.
percent_black_women_killed_to_women

# Claim 3: Unarmed Black women make up 25% of all fatal police shootings of unarmed women. The article says they make up 28% of the unarmed women fatal shootings.
percent_unarmed_black_women_killed_to_unarmed_women




#Alternative way:
#unarmed_women <- black_unarmed_women_killed %>%
 # bind_cols(unarmed_women_killed) %>%
  #mutate(percent_black_unarmed_women_killed = black_unarmed_women/unarmed_women_killed)

#unarmed_women


```

### Sentence 3

* **Sentence text**: “About 31 percent, or 77, of the 247 women fatally shot by police since 2015 had mental health issues, compared to 22 percent of the 5,362 men killed.”
* **Analysis summary**: SKIPPING THIS QUESTION

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 4

* **Sentence text**: “Since The Washington Post began tracking fatal shootings by police in 2015, officers have fatally shot 247 women out of the more than 5,600 people killed overall.”

* **Analysis summary**: Since the time of the article in which the sentence was published, 33 more women have been fatally shot by police and the total of people fatally shot by police has rose to 6,087. 


```{r}
# Put code to reverse engineer sentence here:

total_women_killed <- fatal_police_shootings %>%
  group_by(gender) %>%
  count()
total_killed <- fatal_police_shootings_data %>%
  count()
  

# Display results of code below this codeblock
total_women_killed
total_killed


# Display results of code below this codeblock

```

### Sentence 5

* **Sentence text**: "The starkest difference between men and women is the rate: Women account for about half the population but 4 percent of the killings."

* **Analysis summary**: My findings show that women account for 4.4 percent of killings between male, female and one N/A. My findings are slightly higher than the original question, maybe due to more killings that have happened since this data was published.  There were 5816 men killed, 270 females and 1 N/A. A total of 6,087. Next, divide 270 by 6,087 multiply it by 100 and get 4.44 percent. 


```{r}
# Put code to reverse engineer sentence here

gender_killed <- fatal_police_shootings %>%
 group_by(gender) %>%
 summarise(amount_killed = n()) %>%
 arrange(desc(amount_killed)) %>%
 mutate(total_killed = sum(amount_killed)) %>%
 mutate(pct_total_killed = amount_killed/total_killed*100)


# Display results of code below this codeblock

gender_killed 

```

-30-
